\section{Experience}
\experience{\textbf{PayPal}}{Vancouver, Canada}{Software Engineer, Payouts}{Mar 2023 - Present}
\begin{itemize}[leftmargin=*]
    \item {
        \textbf{Secured GraphQL service against 1 critical vulnerability} by building authentication component that issues and verifies 48 thousand tokens (\href{https://datatracker.ietf.org/doc/html/rfc7519}{RFC 7519}) per day. Used Payara server, HazelCast queue \& cache, MySQL, EclipseLink and EJB dependency injection.
    }
    \item {
        \textbf{Detected an attack, traffic 64 times more than average}, by instrumenting authentication component, building Splunk dashboard and alarms that notified team instantly.
    }
    \item {
        \textbf{Made it possible to triage bugs and solve customer issues} by correlating iOS and Android client events with Payara server logs. Achieved this by augmenting logs with unique identifiers.
    }
    \item {
        \textbf{Sped up authentication latency ($\approx$ 30\%)} by making database calls asynchronous and using cache "\href{https://en.wikipedia.org/wiki/Cache_(computing)#Writing_policies}{write back}" strategy rather than "\href{https://en.wikipedia.org/wiki/Cache_(computing)#Writing_policies}{write through}".
    }
    \item {
        \textbf{Saved 5 days per quarter ($\approx$ 10\%) of developer time and ensured compliance} by designing and implementing a data-driven account registration form using TypeScript, React and GraphQL.
    }
\end{itemize}

\experience{\textbf{Amazon}}{Vancouver, Canada}{Software Engineer, Automated Ads}{Jun 2022 - Mar 2023}
\begin{itemize}[leftmargin=*]
    \item {
        \textbf{Secured alpha-beta ads testing platform} by configuring Apache Tomcat reverse-proxy and creating private networks on AWS; used Cloud Development Kit to authenticate and authorized all internal traffic.
    }
    \item {
        \textbf{Saved 7 days per quarter ($\approx$ 10\%) of developer labour} by automating alpha-beta ads testing using Amazon Event Bridge, SQS, Lambda, and Google Guice dependency injection. Ensured fault tolerance by writing unit and integration tests.
    }
    \item {
        \textbf{Reduced severity-2 tickets ($\approx$ 10\%)} by eliminating “ec2 is out of capacity” errors for Spark clusters using CloudWatch alarms on the number of instances in an availability zone.
    }
\end{itemize}

\experience{\textbf{Visier}}{Vancouver, Canada}{Software Engineer Intern, Build Systems}{May 2021 - Dec 2021}
\begin{itemize}[leftmargin=*]
    \item {
        \textbf{Monitored Gradle task adoption, execution time, and exception frequency} by implementing telemetry plugin. Designed plugin to be fault-tolerant, efficient, and respectful of privacy.
    }
    \item {
        Configured Consul and Docker to \textbf{allow containerized services to discover each other}.
    }
    \item {
        Created Bitbucket plugin to \textbf{notify Slack of pull requests modifying a given file or branch}.
    }
\end{itemize}