\section{Experience}

\outerlist
{
    \entrybig
    {
        \textbf{PayPal}
    }
    {
        Vancouver, Canada
    }
    {
        \textbf{Software Engineer}, Payments
    }
    {
        May 2022, Current
    }
    % \innerlist{
    %     \entry{

    %     }
    % }

    \entrybig
    {
        \textbf{Amazon}
    }
    {
        Vancouver, Canada
    }
    {
        \textbf{Software Engineer}, Automated Ads
    }
    {
        May 2022, January 2023
    }
    \innerlist{
        \entry{
            Built A/B test platform to measure Ad Spend elasticity,
            drafted design documents, collected requirements from scientists, wrote tests, 
            implemented Lambda functions, Apache Tomcat servlets as well as reverse-proxy for authentication and authorization, added alarms and monitors.
            Used Spark, Hadoop, Amazon Web Services, Cloud Development Kit, Guice, Scala and Java.
        }
        \entry{
            Took initiative - built Jinja2 plugin and template for common manual deployment. 
            Reduced manual effort by 30 story points per quarter. Enrolled in On-Call rotations, debugged Spark and Hadoop issues, 
            coordinated with adjacent teams to resolve up-stream issues quickly.
        }
    }
    
    \entrybig
	{
	    \textbf{Visier}
    }
    {
        Vancouver, Canada
    }
	{
	    \textbf{Software Engineer Intern}, Build Systems
    }
    {
        May 2021, December 2021
    }
    
    \innerlist
    {
        \entry
        {
            Implemented Gradle telemetry plugin to monitor task adoption, execution time, and exception frequency. Designed plugin to be fault-tolerant, efficient, and respectful of privacy.
        }
        \entry
        {
            Configured Consul and Docker network to allow containerized services to discover each other.
        }
        \entry
        {
            Created Bitbucket plugin to notify Slack of pull requests modifying a given file or target branch.
        }
    }
    
    \entrybig
	{
	    \textbf{Squarepoint Capital}
    }
    {
        Montreal, Canada
    }
	{
	    \textbf{Software Engineer Intern}, Low Latency Market Data
    }
    {
        May 2020, August 2020
    }
    
    \innerlist
    {
	    \entry
        {
            Developed telemetry framework to monitor hardware and software on hundreds of servers. System alerted service owners if a network interface's "input discards" reach a threshold or a commit degrading performance.
        }
	    \entry
	    {
            Integrated static analysis tool into code review workflow and build pipeline (Cppcheck, Bamboo \& Bitbucket). Resulted in finding and patching invalid memory access errors in feed handler.
        }
    }

    \entrybig
	{
        \textbf{University of British Columbia}
    }
    {
        Vancouver, Canada
    }
	{
        \textbf{Teaching Assistant}, Data Structures \& Algorithms
    }
    {
        January 2020, April 2020
    }
    \innerlist
    {
        \entry
        {
            Debugged students’ programs, taught C++, proved algorithm correctness and analyzed run-times.
        }
    }
}
